---
title: "prediction"
author: "Saptarshi"
date: "10/31/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading packages

```{r, echo=TRUE}
library(caret)
library(rpart)
library(rattle)
```

## Loading dataset


data_train<-read.csv("pml-training.csv",TRUE,",")

dim(data_train)

data_test<- read.csv("pml-testing.csv",TRUE,",")



## Create training and test


training<- createDataPartition(data_train$classe,p=0.7)

trained<- trained[,training]

tested<- tested[,-training] 



## removing first 7 columns because not reqd.

training <- training[, -c(1:7)]


## removing near zero var variables

non_zero_var <- nearZeroVar(training)
trained <- training[,-non_zero_var]


## apply decision tree model on traindata

set.seed(1234)
decisionTree <- rpart(classe ~ ., data=trained, method="class")
fancyRpartPlot(decisionTree)

## Apply on test data

predictTree <- predict(decisionTree, data_test, type = "class")

## Check accuracy

checktree <- confusionMatrix(predictTreeMod1, testData$classe)
checktree



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
